---
title       : "Planning Travels to The Known World?"
subtitle    : "Will you survive the trip?"
author      : Christina Brady
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
github:
  user: christinabrady
  repo: GOT_survival_calc_elevator
---
```{r include = FALSE, cache= FALSE}
load("../project/got_model.RData")
```

As many people may already know, George R. R. Martin's The Known World, is perilous world; 74 of our beloved (and not so) characters have died. Between white walkers, direwolves, the faceless god, the lord of light, dragons, wars, sacrifices and weddings, the odds are not good.  

---


Death, though bountiful, is not entirely unpredictable. If you are planning a trip to The Known World, either for business or pleasure (I hear the beaches of Dorne are amazing). 

---


We created an algorithm to predict your chances of surviving your trip.

---

```{r, echo = FALSE, eval= TRUE}
result1 <- as.numeric(predict(house_mod, newdata = data.frame(house = "nohouse", age = 25, gender = "female", children = "no", war = "no", go_to_wedding = "no"), type = "response"))

result2 <- as.numeric(predict(house_mod, newdata = data.frame(house = "baratheon", age = 65, gender = "male", children = "yes", war = "yes", go_to_wedding = "yes"), type = "response"))
```
For example: If you are 25 year old female, whose last name is Smith and who has no children, no intention to attend a wedding while there and no intention to start a war, your chances of survival are `r round(result1*100)` percent.

On the other hand, if you are a 65 year old male, whose last name is Baratheon, you have particpated in wars, you have many children and you have attended weddings, your chances of survival are `r round(result2*100)` percent.

--- 


Don't take any chances. Find us [here](https://christinabrady.shinyapps.io/project/)


